### 2023-03-17 chapter0/chapter0.tex
Trimmed abstract of some supporting details

\begin{abstract}
\noindent
Living systems are governed by the interactions between large collections of atoms called macromolecules. The most important class of these macromolecules are proteins, which are the molecular machines that carry out a cell's processes. Though proteins are linear chains of simpler building blocks called amino acids, many proteins accomplish their functions by ``folding'' into well-defined three-dimensional structures. This stability makes folded proteins easier to study with various biochemical and bioinformatics techniques, so for many years scientists believed fixed structures were necessary for protein function. By the early 2000s, however, evidence had accumulated that unstructured or ``intrinsically disordered'' regions (IDRs) were ubiquitous in proteins. Furthermore, despite rapidly fluctuating through a range of configurations, these regions were essential for many cellular processes such as signaling and regulation. Although our understanding of the structure and function of IDRs has grown significantly over the past two decades, predicting their functions from their sequences of amino acids remains a significant challenge. Because IDRs are structurally unconstrained, their sequences evolve rapidly and are therefore not amenable to traditional bioinformatics analyses which depend on the precise order of amino acids to make comparisons with known proteins. There is increasing evidence, though, that IDRs conserve distributed features such as their chemical composition or net charge, and a recent study clustered IDRs with similar patterns of conserved features into groups with distinct functions. This study, however, was restricted to IDRs in a set of yeast genomes, so it is unclear if these global relationships between conserved features and function are unique to yeast or a general property of IDR evolution. Thus, in this work I conduct a similar set of evolutionary analyses of IDRs in the genomes of 33 different species of fruit flies, which another essential model organism in molecular biology and genetics research. The analysis is divided into two major sections. In the first, sets of proteins with common ancestry are identified in these genomes, and in the second IDRs in these sets of proteins are analysed with a variety of evolutionary models to detect patterns of conservation.
\end{abstract}

>>>>

\begin{abstract}
\noindent
Living systems are governed by the interactions between large collections of atoms called macromolecules. The most important class of these macromolecules are proteins, which are the molecular machines that carry out a cell's processes. Though proteins are linear chains of simpler building blocks called amino acids, many proteins accomplish their functions by ``folding'' into well-defined three-dimensional structures. For many years scientists believed fixed structures were necessary for protein function, but by the early 2000s, however, evidence had accumulated that unstructured or ``intrinsically disordered'' regions (IDRs) were ubiquitous in proteins. Furthermore, these regions were essential for many cellular processes such as signaling and regulation. Although our understanding of the structure and function of IDRs has grown significantly over the past two decades, predicting their functions from their sequences of amino acids remains a significant challenge. Because IDRs are structurally unconstrained, their sequences evolve rapidly and are therefore not amenable to traditional bioinformatics analyses which depend on the precise order of amino acids to make comparisons with known proteins. There is increasing evidence, though, that IDRs conserve distributed features such as their chemical composition or net charge, and a recent study clustered IDRs with similar patterns of conserved features into groups with distinct functions. This study, however, was restricted to IDRs in a set of yeast genomes, so it is unclear if these global relationships between conserved features and function are unique to yeast or a general property of IDR evolution. Thus, in this work I conduct a similar set of evolutionary analyses of IDRs in the genomes of 33 different species of fruit flies.
\end{abstract}
